---
title: Einlesen von Webseiten mit rvest
output: html_notebook
---

# Overview
source: https://rvest.tidyverse.org/ 

rvest helps you scrape (or harvest) data from web pages. It is designed to work with magrittr to make it easy to express common web scraping tasks, inspired by libraries like beautiful soup and RoboBrowser.

If you’re scraping multiple pages, I highly recommend using rvest in concert with polite. The polite package ensures that you’re respecting the robots.txt and not hammering the site with too many requests.

# Activate libraries
library(tidyverse)
library(magrittr)
library(polite)
library(rvest)

# Usage

## Start by reading a HTML page with read_html():
```{r}
starwars <- read_html("https://rvest.tidyverse.org/articles/starwars.html")
```

## Then find elements that match a css selector or XPath expression using html_elements(). In this example, each <section> corresponds to a different film
```{r}
films <- starwars %>% html_elements("section")
films
```

## Then use html_element() to extract one element per film. Here the title is given by the text inside <h2>
```{r}
title <- films %>% 
  html_element("h2") %>% 
  html_text2()
title
```
## Or use html_attr() to get data out of attributes. html_attr() always returns a string so we convert it to an integer using a readr function
```{r}
episode <- films %>% 
  html_element("h2") %>% 
  html_attr("data-id") %>% 
  readr::parse_integer()
episode
```

# If the page contains tabular data you can convert it directly to a data frame with html_table():
```{r}
html <- read_html("https://en.wikipedia.org/w/index.php?title=The_Lego_Movie&oldid=998422565")

html %>% 
  html_element(".tracklist") %>% 
  html_table()
```

